---
title: "Exploratory analyses of Harvard PM2.5 data"
author: "Ruwan T"
date: "2/19/2021"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
#packages
memory.limit(size=100000)
library(haven)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(tableone)
library(splines)
library(tidycensus)
library(tidyverse)
library(lubridate)
library(AER)
library(knitr)
library(splines)
library(data.table)
library(biglm)
library(speedglm)
library(sp)
library(leaflet)
library(raster)
library(rgdal)
library(geosphere)
library(rgeos)
library(wesanderson)
library(stats)
library(devtools)
library(sf)
library(lme4)
library(glmmADMB)
knitr::opts_chunk$set(message=FALSE,cache=TRUE)
```

### Reading in data
Reading in Harvard PM2.5 data: daily zip code-level estimated mean PM2.5 concentrations from 2010-2016 in California, plus several other variables (population weights, associated census tracts, etc.)

```{r}
harvard <- readRDS("S:/Wildfire-Hoshiko/PHIRE COVARIATE DATA/Data For Analysis/CA_Harvard.rds")
head(harvard)
```

## Histogram and spatial distribution
Histogram of mean of estimated PM2.5 concentrations by zip code.

```{r}
# Calculating zip-level PM2.5 mean and max
ca_zip3 <- as.character(seq(900,961,1))
harvard_zip <- harvard %>%
                group_by(ZIP) %>%
                  summarize(pm25mean = mean(PM25.Mean),
                            pm25max = max(PM25.Mean))
ggplot(data=harvard_zip) +
  geom_histogram(aes(pm25mean),fill="white",color="black") +
  xlab("PM2.5 concentration (micrograms/cubic meter)") +
  ggtitle("Histogram of mean PM2.5 concentrations (California, 2010-2016)")
```
\newpage
Spatial distribution of mean and max PM2.5 concentrations by zip code.
```{r}
ca_zip_map <- st_read("S:/Wildfire-Hoshiko/PHIRE COVARIATE DATA/CA zips/tl_2019_us_zcta510/tl_2019_us_zcta510.shp")
ca_zip_map <- ca_zip_map %>% filter(substr(GEOID10,1,3) %in% ca_zip3) %>% rename(ZIP = GEOID10)
ca_zip_map_merge <- full_join(harvard_zip,ca_zip_map,by=c("ZIP")) # adding PM as attribute to shapefile
ggplot(data = ca_zip_map_merge) + 
  geom_sf(aes(geometry=geometry,fill=pm25mean),lwd=0,color=NA) + 
  ggtitle("Mean PM2.5 by zip code (California, 2010-2016)")
ggplot(data = ca_zip_map_merge) + 
  geom_sf(aes(geometry=geometry,fill=pm25max),lwd=0,color=NA) + 
  ggtitle("Max PM2.5 by zip code (California, 2010-2016)")
```
\newpage

## Regional time series of PM2.5

ZIP3-aggregated PM2.5 time series for several major areas. Aggregation to ZIP3 
level is done by calculating daily mean of PM2.5 across all zips in the ZIP3.

Each time series is followed by a plot of how model fit, according to AIC and BIC,
change with increasing degrees of freedom in the natural cubic spline. The model
is a linear regression with PM2.5 as the outcome and a natural cubic spline smoothing
function of time as the predictor.

$$\text{E[PM2.5] = ns(Date,df)} $$

```{r}
#time series
locations <- c("San Francisco","Sacramento","Redding","Los Angeles","Fresno")
locations_zip3 <-  c(940,958,960,900,937)
dof <- c(7,14,28,42,56,70,84,98,112)
df_per_year <- rep(dof/7,2)
harvard$ZIP3 <- substr(harvard$ZIP,1,3)
harvard_ts <- harvard %>% filter(ZIP3 %in% locations_zip3)
for (i in 1:length(locations_zip3)){
  df <- harvard_ts %>% filter(ZIP3==locations_zip3[i])
  df2 <- df %>% group_by(ZIP3,Date)%>%summarize(pm25 = mean(PM25.Mean))
  print(ggplot(data=df2) + geom_point(aes(x=Date,y=pm25)) + 
          xlab("Date") + ylab("Mean PM2.5") + ggtitle(paste(locations[i],"Daily mean PM2.5 concentration (2010-2016)",sep=": ")))
  aic <- c()
  bic <- c()
  for (j in 1:length(dof)){
    m1 <- lm(pm25 ~ ns(Date,dof[j]),data=df2)
    aic <- c(aic,AIC(m1))
    bic <- c(bic,BIC(m1))
  }
  ic <- c(aic,bic)
  ic_label <- c(rep("AIC",length(dof)),rep("BIC",length(dof)))
  dataframe <- data.frame(ic,ic_label,df_per_year)
  print(ggplot(data=dataframe,aes(x=df_per_year,y=ic,color=ic_label)) +
    geom_point() +
    scale_x_discrete(name ="NCS functions per year",
                     limits=df_per_year) +
    ylab("IC") + ggtitle(paste(locations[i],"spline dof/year vs. AIC, BIC - PM2.5 averaged over zips",sep=": ")))
    aic <- c()
  bic <- c()
  for (j in 1:length(dof)){
    m1 <- lm(PM25.Mean ~ ns(Date,dof[j]),data=df)
    aic <- c(aic,AIC(m1))
    bic <- c(bic,BIC(m1))
  }
  ic <- c(aic,bic)
  ic_label <- c(rep("AIC",length(dof)),rep("BIC",length(dof)))
  dataframe <- data.frame(ic,ic_label,df_per_year)
  print(ggplot(data=dataframe,aes(x=df_per_year,y=ic,color=ic_label)) +
    geom_point() +
    scale_x_discrete(name ="NCS functions per year",
                     limits=df_per_year) +
    ylab("IC") + ggtitle(paste(locations[i],"spline dof/year vs. AIC, BIC - PM2.5 NOT averaged over zips",sep=": ")))
}


```


## No spatial separation by ZIP3 -model fit using all PM2.5 data together
```{r}
aic <- c()
bic <- c()
for (j in 1:length(dof)){
    m2 <- lm(PM25.Mean ~ ns(Date,dof[j]),data=df)
    aic <- c(aic,AIC(m2))
    bic <- c(bic,BIC(m2))
}
ic <- c(aic,bic)
  ic_label <- c(rep("AIC",length(dof)),rep("BIC",length(dof)))
  dataframe <- data.frame(ic,ic_label,df_per_year)
  print(ggplot(data=dataframe,aes(x=df_per_year,y=ic,color=ic_label)) +
    geom_point() +
    scale_x_discrete(name ="NCS functions per year",
                     limits=df_per_year) +
    ylab("IC") + ggtitle("All of CA: spline dof/year vs. AIC, BIC"))

```









