---
title: "Exploring RH greater than 100"
author: "Ruwan T"
date: "2/19/2021"
output: pdf_document
---

```{r setup, include=FALSE}
#packages
memory.limit(size=100000)
library(haven)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(tableone)
library(splines)
library(tidycensus)
library(tidyverse)
library(lubridate)
library(AER)
library(knitr)
library(splines)
library(data.table)
library(biglm)
library(speedglm)
library(sp)
library(leaflet)
library(raster)
library(rgdal)
library(geosphere)
library(rgeos)
library(wesanderson)
library(stats)
library(devtools)
library(sf)
library(lme4)
library(glmmADMB)
```



```{r,cache=TRUE,eval=FALSE,include=FALSE}
### Reading in data
# Reading in Harvard PM2.5 data: daily zip code-level estimated mean PM2.5 concentrations from 2010-2016 in California, plus several other variables (population weights, associated census tracts, etc.)
harvard <- readRDS("S:/Wildfire-Hoshiko/PHIRE COVARIATE DATA/Data for Analysis/CA_Harvard.rds")

head(harvard)
```

## Relative Humidity (RH) > 100

Reading in NOAA data

```{r}
ca_zip3 <- as.character(seq(900,961,1))

noaa <- readRDS("S:/Wildfire-Hoshiko/Wildfire - RThilakaratne/PHIRE_Health_Analysis/data/Data For Analysis/CA_NOAA.rds")
noaa2 <- noaa %>% mutate(gt100 = ifelse(RH.Mean>100,1,0))

# 264 instances of RH>100. These are comprised of 20 unique dates and 152 unique zip codes. As there are several million data points in the full dataset, this issue of RH>100 is quite small

noaa3 <- noaa2 %>% group_by(ZIP) %>% summarize(rh_100 = max(gt100),
                                               mean_rh = mean(RH.Mean))
noaa3 <- noaa3 %>% mutate(zip3 = substr(ZIP,1,3))
ca_zip_map <- st_read("S:/Wildfire-Hoshiko/Wildfire - RThilakaratne/PHIRE_Health_Analysis/data/CA zips/tl_2019_us_zcta510/tl_2019_us_zcta510.shp")
ca_zip_map <- ca_zip_map %>% filter(substr(GEOID10,1,3) %in% ca_zip3) %>% rename(ZIP = GEOID10)
ca_zip_map_merge2 <- full_join(noaa3,ca_zip_map,by=c("ZIP"))
```

\newpage
Map of Mean RH (average of daily estimates over 2010-2018) by zip code. This gives a sense of the baseline spatial distribution of RH.

```{r}
ggplot() + 
  geom_sf(data = ca_zip_map_merge2, aes(geometry=geometry,fill=mean_rh),lwd=0) + 
  ggtitle("Mean RH (over study period, 2010-2016 ) by zip code")
```

\newpage
Map of zip codes with those containing at least 1 RH value above 100 highlighted in blue. 

```{r}
ggplot() + 
  geom_sf(data = ca_zip_map_merge2, aes(geometry=geometry,fill=factor(rh_100)),lwd=0) + 
  ggtitle("RH>100 by zip code")
```

These appear to be mostly along the northern coast, with some inland. Zoomed in maps of Los Angeles and the Bay Area are shown below.

\newpage
Same map but zoomed in on LA.

```{r}
ggplot() + 
  geom_sf(data = ca_zip_map_merge2 %>% filter(zip3 %in% c("900","901","902","903","904","905","906","914","915")), aes(geometry=geometry,fill=factor(rh_100)),lwd=0) + 
  ggtitle("RH>100 by zip code - Los Angeles")
```

\newpage
Same map but zoomed in on the Bay Area.

```{r}
ggplot() + 
  geom_sf(data = ca_zip_map_merge2 %>% filter(zip3 %in% c(seq(940,951,1))), aes(geometry=geometry,fill=factor(rh_100)),lwd=0) + 
  ggtitle("RH>100 by zip code - Bay Area")
```

\newpage
Below is the mean relative humidity on Jan 3, 2010, which was one of the days during which a group of zip codes had an RH>100. Those zip codes are shaded the lightest blue. 

```{r}
#Jan 3 2010
noaa4 <- noaa2 %>% filter(Date=="2010-01-03")
ca_zip_map_merge3 <- full_join(noaa4,ca_zip_map,by=c("ZIP"))
ggplot() + 
  geom_sf(data = ca_zip_map_merge3, aes(geometry=geometry,fill=RH.Mean),lwd=0) + 
  ggtitle("Mean RH by zip code, Jan 3 2010")
```

One can see that these are, spatially, not outliers - there is a gradual color gradient around them suggesting the true values are indeed likely to be very high and do not suggest the values >100 on this day are significant deviations from their true values. It may be reasonable to impute the values as 100.

```{r,eval=FALSE,include=FALSE}
ca_zip3 <- as.character(seq(900,961,1))
harvard_zip <- harvard %>%
                group_by(ZIP) %>%
                  summarize(pm25mean = mean(PM25.Mean),
                            pm25max = max(PM25.Mean))
harvard_summer_zip <- harvard %>%
                filter(month(Date) %in% c(6,7,8)) %>%
                group_by(ZIP) %>%
                  summarize(pm25mean = mean(PM25.Mean),
                            pm25max = max(PM25.Mean))

ca_zip_map <- st_read("S:/Wildfire-Hoshiko/Wildfire - RThilakaratne/PHIRE_Health_Analysis/data/CA zips/tl_2019_us_zcta510/tl_2019_us_zcta510.shp")
ca_zip_map <- ca_zip_map %>% filter(substr(GEOID10,1,3) %in% ca_zip3) %>% rename(ZIP = GEOID10)
ca_zip_map_merge <- full_join(harvard_zip,ca_zip_map,by=c("ZIP"))
# ggplot() + 
#   geom_sf(data = ca_zip_map_merge, aes(geometry=geometry,fill=pm25mean),lwd=0) + 
#   ggtitle("Mean PM2.5 by zip code")
# ggplot() + 
#   geom_sf(data = ca_zip_map_merge, aes(geometry=geometry,fill=pm25max),lwd=0) + 
#   ggtitle("Max PM2.5 by zip code")



```





