---
title: "Comparing lag effects"
author: "Ruwan T"
date: "4/8/2021"
output: word_document
---
```{r,include=FALSE}
#packages
memory.limit(size=100000)
library(arm)
library(haven)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(tableone)
library(splines)
library(tidycensus)
library(tidyverse)
library(lubridate)
library(AER)
library(knitr)
library(data.table)
library(speedglm)
library(sp)
library(leaflet)
library(raster)
library(rgdal)
library(geosphere)
library(rgeos)
library(wesanderson)
library(stats)
library(sf)
library(lme4)
library(weathermetrics)
library(effects)
library(sjPlot)
library(broom.mixed)
library(dlnm)
library(forecast)
library(readxl)
library(biglm)

```

## Reading in data
```{r,cache=TRUE}
# Reading in dataset
data4 <- readRDS("S:/Wildfire-Hoshiko/PHIRE OSHPD DATA/Analytic datasets/FINAL ED and PDD dataset with covariates/Asthma, CV, Resp, COPD ED and PDD data strats with covariates and HMS.rds")

# Data header
head(data4)
# 
zips <- sample(unique(data4$PATZIP),10)
data4 <- data4 %>% filter(PATZIP %in% zips)

unname <- function(x) {
  names(x) <- NULL  
  x
}


```


## Running DLM
```{r,cache=TRUE}
zip3list <- unique(data4$zip3) # getting list of ZIP3's in dataset
pm25_coefs_dlm5_zip3 <- data.frame(matrix(nrow=length(zip3list),ncol=8,NA))  # initializing storage dataframe
for (i in 1:length(zip3list)){ # cycling through list of zip3's
        zip_3 <- as.character(zip3list[i]) # storing current zip3
        subset <- data4 %>% filter(zip3==zip_3) # subsetting to current zip3
        region <- subset$region[1] # identifying corresponding region
        cb05.pm.2 <- crossbasis(subset$pm25, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=subset$PATZIP) # buildling crossbasis (lagged varibales)
        model_dlm_05 <- speedglm(ed_asthma ~ cb05.pm.2 + ns(hi,3) + dow + ns(dayseq,72) + PATZIP + offset(log(popsize)),data = subset,family=poisson(link="log")) # running model
        coefs <- as.character(coef(model_dlm_05)[2:7]) # store PM coefficients
        pm25_coefs_dlm5_zip3[i,] <- c(zip_3,region,coefs) # store zip3, region, and coefs as a row in storage dataframe
        rr <- exp(unname(coef(model_dlm_05)*10)[2:7]) # scaling to 10 unit increase and exponentiating to get RR
        lb <- exp((unname(coef(model_dlm_05))[2:7]-(unname(sqrt(diag(vcov(model_dlm_05))))[2:7])*1.96)*10) # lower 95% CI bound
        ub <- exp((unname(coef(model_dlm_05))[2:7]+(unname(sqrt(diag(vcov(model_dlm_05))))[2:7])*1.96)*10) #upper 95% CI bound
        
        # plotting PM coefficients (same-day and lags) for the current ZIP3
        lag <- c(0,1,2,3,4,5)
        toplot <- data.frame(rr,lb,ub,lag)
        names(toplot) <- c("RR","LB","UB","Lag")
        
        print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
          geom_point() +
          geom_errorbar(aes(ymin=LB,ymax=UB)) +
                ggtitle(paste("ZIP3 ",zip_3,", ",region,":"," 6-day DLM",sep="")))
}
names(pm25_coefs_dlm5_zip3) <- c("ZIP3","Region","Lag0","Lag1","Lag2","Lag3","Lag4","Lag5")
pm25_coefs_dlm5_zip3_2 <- cbind(pm25_coefs_dlm5_zip3[,1:2],exp(sapply(pm25_coefs_dlm5_zip3[,3:8],function(x) as.numeric(x))))
```


## ZIP3 map
```{r,cache=TRUE,eval=FALSE}
# creating ZIP3 map
ZIP3shapes <- readRDS("S:/Wildfire-Hoshiko/PHIRE COVARIATE DATA/ZIP3Shapes.rds")
ZIP3shapes$ZIP3 <- as.numeric(ZIP3shapes$ZIP3)
ZIP3shapesCA <- ZIP3shapes %>% filter(ZIP3<=966 & ZIP3>=900)

```

## comparing zip3's where issue exists vs not
```{r,cache=TRUE,eval=FALSE}
# identifying elevated late lag effect issue (defined as last lag having greater effect than other lags)
pm25_coefs_dlm5_zip3_3 <- pm25_coefs_dlm5_zip3_2 %>% 
                                mutate(issue = ifelse(Lag5>Lag1 & Lag5>Lag2 & Lag5>Lag3 & Lag5>Lag4,1,0),
                                       ZIP3 = as.numeric(ZIP3))

# merging to map
ZIP3shapesCA_issue <- inner_join(ZIP3shapesCA,pm25_coefs_dlm5_zip3_3,by=c("ZIP3"))
ZIP3shapesCA_issue <- ZIP3shapesCA_issue %>% mutate(issue2 = factor(x=issue,levels=c("0","1"),labels = c("No","Yes")))
ggplot() +
  geom_sf(data=ZIP3shapesCA_issue, aes(fill=issue2),color=NA) +
  labs(fill="Lag5 > Lag1-Lag4") +
  ggtitle("Issue of Lag5 being greater than Lags 1-4")


```


## 6-day DLM zip random intercept meta-analytic approach
```{r}
# 6-day DLM meta-analytic approach
zip3list <- unique(data4$zip3)
pm25_coefs_dlm5_zip3 <- data.frame(matrix(nrow=length(zip3list),ncol=14,NA))
for (i in 1:length(zip3list)){
        zip_3 <- as.character(zip3list[i])
        subset <- data4 %>% filter(zip3==zip_3)
        region <- subset$region[1]
        cb05.pm <- crossbasis(subset$pm25, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=subset$PATZIP)
        tic <- Sys.time()
        subset$PATZIP <- as.factor(subset$PATZIP)
        model_dlm_05 <- glmer(ed_asthma ~ cb05.pm + ns(hi,3) + dow + ns(dayseq,72) + (1|PATZIP),data = subset,family=poisson(link="log"),nAGQ = 0)
        toc <- Sys.time()
        toc-tic
        coefs <- (unname(fixef(model_dlm_05))*10)[2:7] # save coefs
        se <- (unname(se.fixef(model_dlm_05))*10)[2:7] # save SE's
        pm25_coefs_dlm5_zip3[i,] <- c(zip_3,region,coefs,se) # store in dataframe
        
        # plot risk
        rr <- exp((unname(fixef(model_dlm_05))*10)[2:7])
        lb <- exp( (unname(fixef(model_dlm_05))*10)[2:7] - (unname(se.fixef(model_dlm_05))*10)[2:7])
        ub <- exp( (unname(fixef(model_dlm_05))*10)[2:7] + (unname(se.fixef(model_dlm_05))*10)[2:7])

        lag <- c(0,1,2,3,4,5)
        toplot <- data.frame(rr,lb,ub,lag)
        names(toplot) <- c("RR","LB","UB","Lag")

        print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
          geom_point() +
          geom_errorbar(aes(ymin=LB,ymax=UB)) +
                ggtitle(paste("ZIP3 ",zip_3,", ",region,":"," 6-day DLM",sep="")))
        print(i)

}
names(pm25_coefs_dlm5_zip3) <- c("ZIP3","Region","PE_Lag0","PE_Lag1","PE_Lag2","PE_Lag3","PE_Lag4","PE_Lag5","SE_Lag0","SE_Lag1","SE_Lag2","SE_Lag3","SE_Lag4","SE_Lag5")

# meta analysis
results <- pm25_coefs_dlm5_zip3
results <- cbind(results[,1:2],sapply(results[,3:14],function(x) as.numeric(x)))

# random effects meta analysis to get overall effects by lag
lag0 <- meta.summaries(d=results$PE_Lag0,se=results$SE_Lag0,method="random",logscale=TRUE)
lag1 <- meta.summaries(d=results$PE_Lag1,se=results$SE_Lag1,method="random",logscale=TRUE)
lag2 <- meta.summaries(d=results$PE_Lag2,se=results$SE_Lag2,method="random",logscale=TRUE)
lag3 <- meta.summaries(d=results$PE_Lag3,se=results$SE_Lag3,method="random",logscale=TRUE)
lag4 <- meta.summaries(d=results$PE_Lag4,se=results$SE_Lag4,method="random",logscale=TRUE)
lag5 <- meta.summaries(d=results$PE_Lag5,se=results$SE_Lag5,method="random",logscale=TRUE)

# plotting meta analyzed effects
rr <- c(exp(lag0$summary),exp(lag1$summary),exp(lag2$summary),exp(lag3$summary),exp(lag4$summary),exp(lag5$summary))
lb <- c(exp(lag0$summary-1.96*lag0$se.summary),exp(lag1$summary-1.96*lag1$se.summary),exp(lag2$summary-1.96*lag2$se.summary),exp(lag3$summary-1.96*lag3$se.summary),exp(lag4$summary-1.96*lag4$se.summary),exp(lag5$summary-1.96*lag5$se.summary))
ub <- c(exp(lag0$summary+1.96*lag0$se.summary),exp(lag1$summary+1.96*lag1$se.summary),exp(lag2$summary+1.96*lag2$se.summary),exp(lag3$summary+1.96*lag3$se.summary),exp(lag4$summary+1.96*lag4$se.summary),exp(lag5$summary+1.96*lag5$se.summary))

lag <- c(0,1,2,3,4,5)
toplot <- data.frame(rr,lb,ub,lag)
names(toplot) <- c("RR","LB","UB","Lag")

print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
  geom_point() +
  geom_errorbar(aes(ymin=LB,ymax=UB)) +
  ggtitle("6-day DLM summary effects and confidence intervals"))
```

## Creating randomized PM2.5 within each zip
```{r,eval=FALSE}
time_series <- data.frame(data4[,c("PATZIP","serv_dt","pm25_residual_cz")]) # extracting PM residaul time series
zips <- unique(time_series$PATZIP) # save zips to cycle through for randomization (want to do randomization within each zip time series, not across)
time_series_random <- c()
for (i in 1:length(zips)){
  sub <- time_series %>% filter(PATZIP==zips[i])
  sub[,"pm25_residual_cz"] <- sample(sub[,"pm25_residual_cz"]) # randomization (randomly sampling without replacement)
  time_series_random <- rbind(time_series_random,sub)
  print(i)
}
names(time_series_random) <- c("PATZIP","serv_dt","pm25_residual_cz_rand")
#merge back with dataset
data5 <- inner_join(data4,time_series_random,by=c("PATZIP","serv_dt"))
data6 <- data5 %>% filter(region=="San Diego - Main")
```

## 6-day DLM zip random intercept single model approach
```{r,eval=FALSE}
# original PM2.5
cb05.pm <- crossbasis(data5$pm25_residual_cz, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=data5$PATZIP)
        model_dlm_05 <- glmer(ed_asthma ~ cb05.pm + ns(hi,3) + dow + ns(dayseq,36) + (1|PATZIP),data = data5,family=poisson(link="log"),nAGQ = 0)

 rr <- exp((unname(fixef(model_dlm_05))*10)[2:7])
        lb <- exp( (unname(fixef(model_dlm_05))*10)[2:7] - (unname(se.fixef(model_dlm_05))*10)[2:7])
        ub <- exp( (unname(fixef(model_dlm_05))*10)[2:7] + (unname(se.fixef(model_dlm_05))*10)[2:7])
        
        lag <- c(0,1,2,3,4,5)
        toplot <- data.frame(rr,lb,ub,lag)
        names(toplot) <- c("RR","LB","UB","Lag")
        
        print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
          geom_point() +
          geom_errorbar(aes(ymin=LB,ymax=UB)) +
             ylim(0.99, 1.05) +
                ggtitle("6-day DLM: Zip code random intercept model"))
```

## 6-day DLM zip random intercept model approach, randomized time series
```{r,eval=FALSE}


cb05.pm <- crossbasis(data5$pm25_residual_cz_rand, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=data5$PATZIP) # creating crossbasis from randomized PM time series
TIC <- Sys.time()
model_dlm_5_rand <- glmer(ed_asthma ~ cb05.pm + ns(hi,3) + dow + ns(dayseq,36) + (1|PATZIP),data = data5,family=poisson(link="log"),nAGQ = 0)
TOC <- Sys.time()
TOC-TIC

rr <- exp((unname(fixef(model_dlm_5_rand))*10)[2:7])
lb <- exp( (unname(fixef(model_dlm_5_rand))*10)[2:7] - (unname(se.fixef(model_dlm_5_rand))*10)[2:7])
ub <- exp( (unname(fixef(model_dlm_5_rand))*10)[2:7] + (unname(se.fixef(model_dlm_5_rand))*10)[2:7])

lag <- seq(0,5)
toplot <- data.frame(rr,lb,ub,lag)
names(toplot) <- c("RR","LB","UB","Lag")

print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
  geom_point() +
  geom_errorbar(aes(ymin=LB,ymax=UB)) +
             ylim(0.99, 1.05) +
        ggtitle("6-day DLM: Zip code random intercept model, randomized PM"))



```

## 6-day DLM zip3 + offset(log(popsize)) model approach
```{r,eval=FALSE}
# original PM2.5
cb05.pm <- crossbasis(data5$pm25_residual_cz, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=data5$PATZIP)
        model_dlm_05_old <- speedglm(ed_asthma ~ cb05.pm + ns(hi,3) + dow + zip3 + ns(dayseq,36) + offset(log(popsize)),data = data5,family=poisson(link="log"))

 rr <- exp(unname(coef(model_dlm_05_old)*10)[2:7])
lb <- exp((unname(coef(model_dlm_05_old))[2:7]-(unname(sqrt(diag(vcov(model_dlm_05_old))))[2:7])*1.96)*10)
ub <- exp((unname(coef(model_dlm_05_old))[2:7]+(unname(sqrt(diag(vcov(model_dlm_05_old))))[2:7])*1.96)*10)
        
        lag <- c(0,1,2,3,4,5)
        toplot <- data.frame(rr,lb,ub,lag)
        names(toplot) <- c("RR","LB","UB","Lag")
        
        print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
          geom_point() +
          geom_errorbar(aes(ymin=LB,ymax=UB)) +
             ylim(0.99, 1.05) +
                ggtitle("6-day DLM: zip3 + offset(log(popsize)) model"))
```

## 6-day DLM zip3 + offset(log(popsize)) model approach, randomized time series
```{r,eval=FALSE}


cb05.pm <- crossbasis(data5$pm25_residual_cz_rand, lag=5, argvar=list(fun="lin"),arglag=list(fun="integer"),group=data5$PATZIP) # creating crossbasis from randomized time series
TIC <- Sys.time()
model_dlm_5_rand_old <- speedglm(ed_asthma ~ cb05.pm + ns(hi,3) + dow + zip3 + ns(dayseq,36) + offset(log(popsize)) ,data = data5,family=poisson(link="log"))
TOC <- Sys.time()
TOC-TIC

 rr <- exp(unname(coef(model_dlm_5_rand_old)*10)[2:7])
lb <- exp((unname(coef(model_dlm_5_rand_old))[2:7]-(unname(sqrt(diag(vcov(model_dlm_5_rand_old))))[2:7])*1.96)*10)
ub <- exp((unname(coef(model_dlm_5_rand_old))[2:7]+(unname(sqrt(diag(vcov(model_dlm_5_rand_old))))[2:7])*1.96)*10)

lag <- seq(0,5)
toplot <- data.frame(rr,lb,ub,lag)
names(toplot) <- c("RR","LB","UB","Lag")

print(ggplot(data=toplot,aes(x=Lag,y=RR)) +
  geom_point() +
  geom_errorbar(aes(ymin=LB,ymax=UB)) +
             ylim(0.99, 1.05) +
        ggtitle("6-day DLM: zip3 + offset(log(popsize)) model, randomized PM"))



```






